Final Project Submission

### 2021-05-12 code/Submission.Rmd
done

```{r central_fig, echo = echoval}
levels(pew$PUBLICDATA_W49) <- c("More Important To Find Others' Information","More Important To Keep Their Own\nInformation Private", "Refused")
pew %>% drop_na(PUBLICDATA_W49) %>% drop_na(sumRTBF) %>% filter(PUBLICDATA_W49 != "Refused") %>% ggplot(aes(x = sumRTBF, fill = as.factor(sumRTBF))) +
  geom_bar(position = "dodge", color = 'black') +
  labs (
    title = "Attitudes on How Many Categories of Data Should Be Protected by\n\"The Right To Be Forgotten\" Split by Stance on Personal Data Use",
    x = "How many of the following categories fall under the Right to Be Forgotten?\n-Data collected by law enforcement   -Employment history or work record\n   -Negative media coverage   -Potentially embarassing photos or videos",
    y = "",
    caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"
  ) +
  scale_fill_brewer(palette="YlGnBu") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        legend.position = "none") + 
  facet_wrap(~PUBLICDATA_W49)
```

@@

## Generate Title
title2 <- "Trust In Responsible Use Of Facial Recognition Tech\nFaceted on Tech Literacy"

###Data Viz###
## Centerd, No Percents 
plot(likert(df_f3.reverse[,c(1:3)], grouping = df_f3.reverse[,4]), legend.position="right", centered = TRUE, plot.percents=TRUE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE, center = 2.5) + 
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = c("Not at all", "Not too much", "Somewhat", "A great deal")) + #order and color the likert boxes
  ggtitle(title2) +
  labs(caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy")+
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend
```

### Explanation of Key Figure 2
From a purely theoretical point of view, facial recognition technology represents a huge privacy risk to the general public. Any image -- be it a photo posted online or a single frame taken from a public CCTV camera -- can be used to accurately identify any individual by simply running a facial recognition program. Currently, if someone wants to reliably identify a person, they either have seen their face beforehand or they need to manually match to a known face in a face-identity repository. Facial recognition removes the former limitation and speeds up the latter exponentially by searching for a match in hundreds of thousands of faces extremely quickly (Venema, 2020). As a result, one’s anonymity is eroded away as there are multitudes of cameras in urban spaces (Smithsimon, 2003) whose data can be fed to a facial recognition system .

When we reify the issue of facial recognition technology by limiting it to the capabilities of current technological systems, the risk posed by facial recognition adds a new level of dimensionality. Current facial recognition systems are far from accurate and are plagued with issues of bias in their datasets (Buolamwini & Gebru, 2018). These systems are trained to recognize primarily white, cisgender male faces -- meaning that they perform poorly on everyone else. Indeed, to highlight this issue, the ACLU ran the faces of the 115th United States Congress through Amazon’s off the shelf facial recognition tool called “Rekognition.” Amazon Rekognition identified 28 members of Congress as “other people who have been arrested for a crime.” Of those false matches“40 percent…were of people of color, even though they make up only 20 percent of Congress” (Snow, 2018).

In short, facial recognition in the early 21st century is a highly flawed tool that outputs racist results and is a threat to the privacy of the general public. Currently, there is no national regulation of facial recognition technology (Crawford, 2019). However, public opinion of facial recognition technology can shape policy which can lead to privacy protections. This is why key figure 2 is important because it sheds light on how much trust a (somewhat) representative sample of the American people have in different groups using facial recognition technology.

Rather than just display the preexisting results from the Likert scale in the Pew survey, we decided to partition the data based off of how knowledgeable the respondent was about technology. The Pew survey had ten questions assessing each respondent’s knowledge on topics ranging from what the ‘s’ in ‘https’ means to how social media platforms generate revenue. Four of these questions -- “Which of the following is the largest source of revenue for most major social media platforms?”, “Where might someone encounter a phishing scam?”, “Which two companies listed below are both owned by Facebook?”, and a question asking respondents to identify a picture of Twitter co-founder Jack Dorsey -- were excluded because they were not directly related to measuring a respondent’s knowledge of how technology worked on a technical or legal level. Thus, each respondent received a literacy score between zero and six; this score was the sum of the number of questions the respondent answered correctly. Additional figure 1 for key figure 2 visualizes the underlying distribution of literacy scores.

The literacy scores are then binned into three levels -- “No Literacy,” “Some Literacy,” and “High Literacy” -- because visualizing all six levels had a poor data-to-ink ratio. The category of “No Literacy” consists solely of respondents who scored a zero out of 6, the category of Some Literacy consists of respondents whose scores ranged from a two out of six to a four out of six, and the category of High Literacy consists of respondents who scored either a five out of six or six out of six. Additional figure 2 for key figure 2 visualizes how the literacy scores are encapsulated by the binning. 
After a cursory glance it is clear to see that this binning scheme puts an emphasis on those who knew nothing about the technical and legal aspects of technology. We felt that this was important to highlight because those who have no literacy are numerous and likely have a different perspective than those who have some tech literacy. We choose not to put an emphasis on those with a perfect score because the six questions we have to compute a tech literacy score measure a limited scope of knowledge and the difference between getting five or six questions correct is not as significant as the difference between answering zero or one questions correctly.

@@

The ranking preference across the facets, however, is concerning. Many experts call for a ban of facial recognition use (Bennett, 2011) (Crawford, 2019). This does not line up with public opinion. From a perspective of a trust-distrust dichotomy, key figure 2 indicates that -- at best -- seems to be public support for regulation on tech companies and advertisers since a majority of respondents distrust them. Unfortunately, regulation of law enforcement use seems less likely as a majority of respondents, regardless of literacy level, trust them to use facial recognition responsibly.
One possible explanation for the difference between expert opinion and public sentiment is that the respondents of the survey have a poor understanding of the limitations of facial recognition technology as seen in Additional figure 3 for key figure 2. They believe accurately identify people, assess gender, and assess race. They are incorrect  (Buolamwini & Gebru, 2018) (Crawford, 2019).

@@

@@

Smithsimon, M. (2003, Winter). Private Lives, Public Spaces: The Surveillance State. *Dissent*, *50*(1), 43.

@@

```{r kf1-appendix-1, echo=echoval}
levels(pew$PUBLICDATA_W49) <- c("Find others' information","Keep their own information private", "Refused")
pew %>% drop_na(PUBLICDATA_W49) %>% filter(PUBLICDATA_W49 != "Refused") %>% ggplot(aes(x = PUBLICDATA_W49)) +
  geom_bar(fill="#47b7c3", color = 'black') +
  labs (
    title = "Count of PUBLICDATA Responses",
    subtitle = "Do you think it is more important for people to have the ability to...",
    x = "Responses",
    y = "Counts",
    caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"
  ) + theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(), 
            axis.line = element_line(colour = "black"))
```

@@

```{r kf1-appendix-2, echo=echoval}
pew %>% drop_na(sumRTBF) %>% ggplot(aes(x = sumRTBF)) +
  geom_histogram(binwidth = 1, fill = "#a3d9b5", color = 'black') +
  labs (
    title = "Histogram of RTBF",
    subtitle = "How much do people think we have the right to forget?",
    x = "Number of acceptable categories to forget",
    y = "Count",
    caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"
  ) + theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(), 
            axis.line = element_line(colour = "black"))
```

@@

```{r KNOW-Counts, echo=echoval, out.height="50%"}
pew %>% ggplot(aes(x =sumKnowFactor, fill = groupKnow)) +
  geom_bar(position = 'dodge', color = 'black') +
  scale_fill_brewer(palette = "Blues") +
  labs(
    title = "Distribution of Tech Literacy Scores",
    subtitle = "How Many Out Of The Six Tech Literacy Questions Did Respondents Get Correct",
    y = "Counts",
    x = "Literacy Category",
    fill = "Respondent's\nLiteracy Score",
    caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"
  ) +  
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

@@

@@

```{r FACE2_Bar, echo=echoval, message=FALSE}
pew %>% filter(FACE1_W49 != "Refused") %>% ggplot(aes(x = groupKnow, fill = FACE1_W49)) +
  geom_bar(position = 'dodge', color = 'black') +
  scale_fill_brewer(palette = "Dark2") +
  labs(
    title = "Respondent's Self Reported Familiarity With Facial Recognition",
    y = "Counts",
    x = "Literacy Category",
    fill = "How Much The Respondent\nKnows About Facial Recognition",
    caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"
  ) +  
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
```

@@

## Generate Title
titlef2 <- "How Effective Do Respondents Think Facial Recognition Is\nFaceted on Tech Literacy"

###Graph The Likert Data###
plot(likert(df_f2.reverse[,c(1:3)], grouping = df_f2.reverse[,4]), legend.position="right", centered = TRUE, plot.percents=TRUE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE, center = 2.5) + 
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = rev(levels(df_f2$`Accurately identifying individual people`))) + #order and color the likert boxes
  ggtitle(titlef2) +
    labs(caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy")+
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend

##100 Pcnt bar chart
plot(likert(df_f2[,c(1:3)], grouping = df_f2.reverse[,4]), legend.position="right", centered = FALSE, plot.percents=TRUE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE, center = 2.5) + 
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = rev(levels(df_f2$`Accurately identifying individual people`))) + #order and color the likert boxes
  ggtitle(titlef2) +
    labs(caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy")+
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend
```

@@

titlef4 <- "Opinions on Facial Recognition Use Faceted on Tech Litercay"

###Graph The Likert Data###
plot(likert(df_f4.reverse[,c(1:4)], grouping = df_f4.reverse[,5]), legend.position="right", plot.percents=FALSE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE, center = 1.5) +
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = c("NA", "Not sure", "Unacceptable", "Acceptable")) + #order and color the likert boxes
  ggtitle(titlef4) +
    labs(caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy")+
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend

##100 Pcnt bar chart
plot(likert(df_f4.reverse2[,c(1:4)], grouping = df_f4.reverse[,5]), legend.position="right", centered = FALSE, plot.percents=FALSE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE,) +
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = c("NA", "Not sure", "Unacceptable", "Acceptable")) + #order and color the likert boxes
  ggtitle(titlef4) +
    labs(caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy")+
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend
```

@@

First, to echo Bourdieu’s writings, we would like to problematize our use of the idea of “the public” at all; the data we have been manipulating, and the visualizations produced therein, are by no means necessarily representative of “the public.” The public, as we would like to think of it, does not exist. Per the topline we received as part of this data set, the *actual* body of people surveyed is 5,869 members of the American Trends Panel: a national, probability-based online panel of non-institutionalized adults living in households in the United States, including Alaska and Hawaii. The fact that this is a pre-selected, probability-based panel highlights that the body of participants does not encompass every single person living in the United States, nor does every person living in the United States who interacts in some meaningful way with technology and digital privacy fall under those categorizations. Pew Research Center is a meticulous, thorough group known for producing robust data as well as analyses of said data. Though, there will always be blind spots, which we must be mindful of when discussing* what* exactly our work produced.

@@

As I emphasized in the original text introducing my image, there were two factors that I found it extremely important to accurately represent within my visual examining respondents’ stance on digital privacy and personal data: the scale of the difference between counts for the two binary options to `PUBLICDATA_W49`, and the internal distribution for each of those two categories of respondents on the issue of the Right to Be Forgotten.

I chose fairly quickly to forgo what I would think of as the “reverse” of my final visual: a faceted bar chart broken up by the four categories of information that the survey proposed as falling under the Right to Be Forgotten, showing the breakdown of each category of data’s response along the lines of those who prefer public versus private data. Though this visualization would have the advantage of showing a finer-grained understanding of the Right to Be Forgotten (showing each category directly rather than using a dummy variable of sum counts, as I ultimately did) it ultimately did not reveal anything new or interesting about the `PUBLICDATA_W49` responses. Every single response of counts only reflected the same relationship between public and private stances. This helped me narrow down my work to try and prioritize showing internal distinctions between those two categories instead.

A visualization that I considered, but rejected, is one which uses not a dodged bar chart but a stacked one, showing the two categories of public versus private data people as two bars and having those bars be partitioned accordingly to reflect the internal distribution of counts of categories that should be protected. This visualization looks as follows:

```{r central_fig_alt, echo = echoval}
levels(pew$PUBLICDATA_W49) <- c("Find others'\ninformation","Keep their\nown information\nprivate", "Refused")
pew %>% drop_na(PUBLICDATA_W49) %>% drop_na(sumRTBF) %>% filter(PUBLICDATA_W49 != "Refused") %>% ggplot(aes(x = PUBLICDATA_W49, fill = as.factor(sumRTBF))) +
  geom_bar() +
  labs (
    title = "Attitudes on How Many Categories of Data Should Be Protected by\n\"The Right To Be Forgotten\" by Stance on Personal Data",
    x = "Participants find it more important to...",
    y = "",
    caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"
  ) +
  scale_fill_brewer(palette="YlGnBu", name = "How many of the following categories\nof data should fall under the Right To Be Forgotten:\n   -Data collected by law enforcement\n   -Employment history or work record\n   -Negative media coverage\n   -Potentially embarassing photos or\n     videos", labels=c("None","One","Two","Three","Four"))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))
```
This visualization does both things that I would like it to do: it makes immediately apparent the difference in scale between those who prioritize public data versus private, and it has a clear color-coded breakdown of how many categories of data each class thinks should be protected. However, it is clunky and makes it harder to closely examine the distribution of sum counts than it is in my final graphic. As Healy breaks down, bad design is plagued by bad perception; stacking the boxes for each number makes it hard to directly compare the distribution of counts by not having a common base. This in turn warps our perception of the final data. So while this tells a similar story to the one up above, I ended up making additional aesthetic decisions to better convey that information in a clear and pleasing way.

@@

Jake and Adriana are best of friends and have split the work evenly. [THIS IS A PLACEHOLDER].

>>>>

```{r central_fig, echo = echoval}
levels(pew$PUBLICDATA_W49) <- c("More Important To Find Others' Information","More Important To Keep Their Own\nInformation Private", "Refused")
pew %>% drop_na(PUBLICDATA_W49) %>% drop_na(sumRTBF) %>% filter(PUBLICDATA_W49 != "Refused") %>% ggplot(aes(x = sumRTBF, fill = as.factor(sumRTBF))) +
  geom_bar(position = "dodge", color = 'black') +
  labs (
    title = "Key Figure 1:",
    subtitle = "Attitudes on How Many Categories of Data Should Be Protected by\n\"The Right To Be Forgotten\" Split by Stance on Personal Data Use",
    x = "How many of the following categories fall under the Right to Be Forgotten?\n-Data collected by law enforcement   -Employment history or work record\n   -Negative media coverage   -Potentially embarassing photos or videos",
    y = "",
    caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy")+
  scale_fill_brewer(palette="YlGnBu") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        legend.position = "none") + 
  facet_wrap(~PUBLICDATA_W49)
```

@@

## Generate Title
title2 <- "Trust In Responsible Use Of Facial Recognition Tech\nGrouped By Tech Literacy"

###Data Viz###
## Centerd, No Percents 
plot(likert(df_f3.reverse[,c(1:3)], grouping = df_f3.reverse[,4]), legend.position="right", centered = TRUE, plot.percents=TRUE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE, center = 2.5) + 
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = c("Not at all", "Not too much", "Somewhat", "A great deal")) + #order and color the likert boxes
  ggtitle(title2) +
  labs(title = "Key Figure 2:",
    subtitle = title2,
    caption = "This graph shows a representative sample of the US population’s trust in the\nresponsible use of facial recognition across three different groups.\nIt is clear to see that people trust law enforcement even though law enforcement\nboth has a history of abusing facial recognition technology\n and that current facial recognition systems\n are highly flawed and struggle to accurately identify people of color.\n\nData sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy")+
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend

### Explanation of Key Figure 2
Current facial recognition systems are far from accurate and are plagued with issues of bias in their datasets (Buolamwini & Gebru, 2018). These systems are built to search for a match in hundreds of thousands of faces extremely quickly (Venema, 2020), however, they are trained to recognize primarily white, cisgender male faces -- meaning that they perform poorly on everyone else. Indeed, to highlight this issue, the ACLU ran the faces of the 115th United States Congress through Amazon’s off the shelf facial recognition tool called “Rekognition.” Amazon Rekognition identified 28 members of Congress as “other people who have been arrested for a crime.” Of those false matches “40 percent…were of people of color, even though they make up only 20 percent of Congress” (Snow, 2018).

In short, facial recognition in the early 21st century is a highly flawed tool that outputs racist results and is a threat to the privacy of the general public. Currently, there is no national regulation of facial recognition technology (Crawford, 2019). However, public opinion of facial recognition technology can shape policy which can lead to privacy protections. It is therefore vitally important to understand how public opinion differs for various groups using facial recognition technology.

Rather than just display the preexisting results from the Likert scale in the Pew survey, we decided to partition the data based off of how knowledgeable the respondent was about technology; in other words, we quantified their tech literacy. An in-depth explanation about how and why this tech literacy variable was created can be found with the accompanying explanation of additional figure 1 for key figure 2.

@@

The ranking preference across the facets, however, is concerning. Many experts call for a ban of facial recognition use (Bennett, 2011) (Crawford, 2019) because they do not trust that the technology can be used responsibly by any party. This does not line up with public opinion. From a perspective of a trust-distrust dichotomy, key figure 2 indicates that a majority of respondents only have an overwhelming distrust of advertisers. In addition, the respondents on the whole have more distrust than trust for tech companies to use facial recognition responsibly with the respondents with no tech literacy dead even with 50% trust and 50% distrust. The most concerning finding here, however, is that the majority of respondents, regardless of literacy level, trust law enforcement to use facial recognition responsibly. This is very concerning as law enforcement both has a history of abusing facial recognition technology (Devich-Cyril, 2020) and that, as mentioned above, current facial recognition systems are highly flawed and struggle to accurately identify people of color. This glut of trust for law enforcement – especially as compared to the dearth of trust for advertisers -- could indicate a relative unwillingness to regulate law enforcement’s use of facial recognition technology. 
One possible explanation for the difference between expert opinion and public sentiment is that the respondents of the survey have a poor understanding of the limitations of facial recognition technology as seen in Additional figure 3 for key figure 2. They believe accurately identify people, assess gender, and assess race. They are incorrect (Buolamwini & Gebru, 2018) (Crawford, 2019).

@@

Devich-Cyril, M. (2020, July 5). *Defund Facial Recognition*. The Atlantic. https://www.theatlantic.com/technology/archive/2020/07/defund-facial-recognition/613771/

@@

@@

```{r kf1-appendix-1, echo=echoval}
levels(pew$PUBLICDATA_W49) <- c("Find others' information","Keep their own information private", "Refused")
pew %>% drop_na(PUBLICDATA_W49) %>% filter(PUBLICDATA_W49 != "Refused") %>% ggplot(aes(x = PUBLICDATA_W49)) +
  geom_bar(fill="#47b7c3", color = 'black') +
  labs (
    title = "Count of PUBLICDATA Responses",
    subtitle = "Do you think it is more important for people to have the ability to...",
    x = "Responses",
    y = "Counts",
       caption = c("Additional Figure 1\nFor Key Figure 1",  "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"))+
  theme(plot.caption = element_text(hjust=c(0, 1))) + 
  theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(), 
            axis.line = element_line(colour = "black"))
```

@@

```{r kf1-appendix-2, echo=echoval}
pew %>% drop_na(sumRTBF) %>% ggplot(aes(x = sumRTBF)) +
  geom_histogram(binwidth = 1, fill = "#a3d9b5", color = 'black') +
  labs (
    title = "Histogram of RTBF",
    subtitle = "How much do people think we have the right to forget?",
    x = "Number of acceptable categories to forget",
    y = "Count",
       caption = c("Additional Figure 2\nFor Key Figure 1",  "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"))+
  theme(plot.caption = element_text(hjust=c(0, 1))) +
  theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(), 
            axis.line = element_line(colour = "black"))
```

@@

```{r KNOW-Counts, echo=echoval, out.height="50%"}
pew %>% ggplot(aes(x =sumKnowFactor, fill = groupKnow)) +
  geom_bar(position = 'dodge', color = 'black') +
  scale_fill_brewer(palette = "Blues") +
  labs(
    title = "Distribution of Tech Literacy Scores",
    subtitle = "How Many Out Of The Six Tech Literacy Questions Did Respondents Get Correct",
    y = "Counts",
    x = "Literacy Category",
    fill = "Respondent's\nLiteracy Score",
       caption = c("Additional Figure 1\nFor Key Figure 2",  "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"))+
  theme(plot.caption = element_text(hjust=c(0, 1))) + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

@@

We decided to create a dummy variable that reflected how knowledgeable the respondent was about technology. The Pew survey had ten questions assessing each respondent’s knowledge on topics ranging from what the ‘s’ in ‘https’ means to how social media platforms generate revenue. Four of these questions -- “Which of the following is the largest source of revenue for most major social media platforms?”, “Where might someone encounter a phishing scam?”, “Which two companies listed below are both owned by Facebook?”, and a question asking respondents to identify a picture of Twitter co-founder Jack Dorsey -- were excluded because they were not directly related to measuring a respondent’s knowledge of how technology worked on a technical or legal level. Thus, each respondent received a literacy score between zero and six; this score was the sum of the number of questions the respondent answered correctly. The above figure, additional figure 1 for key figure 2, visualizes the underlying distribution of literacy scores.

The literacy scores are then binned into three levels -- “No Literacy,” “Some Literacy,” and “High Literacy” -- because visualizing all six levels had a poor data-to-ink ratio. The category of “No Literacy” consists solely of respondents who scored a zero out of 6, the category of Some Literacy consists of respondents whose scores ranged from a two out of six to a four out of six, and the category of High Literacy consists of respondents who scored either a five out of six or six out of six. The color in the above figure visualizes how the literacy scores are encapsulated by the binning.

After a cursory glance it is clear to see that this binning scheme puts an emphasis on those who knew nothing about the technical and legal aspects of technology. We felt that this was important to highlight because those who have no literacy are numerous and likely have a different perspective than those who have some tech literacy. We choose not to put an emphasis on those with a perfect score because the six questions we have to compute a tech literacy score measure a limited scope of knowledge and the difference between getting five or six questions correct is not as significant as the difference between answering zero or one questions correctly.

@@

```{r FACE2_Bar, echo=echoval, message=FALSE}
pew %>% filter(FACE1_W49 != "Refused") %>% ggplot(aes(x = groupKnow, fill = FACE1_W49)) +
  geom_bar(position = 'dodge', color = 'black') +
  scale_fill_brewer(palette = "Dark2") +
  labs(
    title = "Respondent's Self Reported Familiarity With Facial Recognition",
    y = "Counts",
    x = "Literacy Category",
    fill = "How Much The Respondent\nKnows About Facial Recognition",
       caption = c("Additional Figure 2\nFor Key Figure 2",  "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"))+
  theme(plot.caption = element_text(hjust=c(0, 1))) + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
```

@@

## Generate Title
titlef2 <- "How Effective Do Respondents Think Facial Recognition Is\nGrouped By Tech Literacy"

###Graph The Likert Data###
plot(likert(df_f2.reverse[,c(1:3)], grouping = df_f2.reverse[,4]), legend.position="right", centered = TRUE, plot.percents=TRUE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE, center = 2.5) + 
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = rev(levels(df_f2$`Accurately identifying individual people`))) + #order and color the likert boxes
  ggtitle(titlef2) +
    labs(caption = c("Additional Figure 3\nFor Key Figure 2",  "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"))+
  theme(plot.caption = element_text(hjust=c(0, 1))) +
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend

##100 Pcnt bar chart
plot(likert(df_f2[,c(1:3)], grouping = df_f2.reverse[,4]), legend.position="right", centered = FALSE, plot.percents=TRUE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE, center = 2.5) + 
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = rev(levels(df_f2$`Accurately identifying individual people`))) + #order and color the likert boxes
  ggtitle(titlef2) +
    labs(caption = c("Additional Figure 3.5\nFor Key Figure 2",  "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"))+
  theme(plot.caption = element_text(hjust=c(0, 1))) +
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend
```

@@

titlef4 <- "Opinions on Facial Recognition Use Grouped By Tech Litercay"

###Graph The Likert Data###
plot(likert(df_f4.reverse[,c(1:4)], grouping = df_f4.reverse[,5]), legend.position="right", plot.percents=FALSE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE, center = 1.5) +
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = c("NA", "Not sure", "Unacceptable", "Acceptable")) + #order and color the likert boxes
  ggtitle(titlef4) +
    labs(caption = c("Additional Figure 4\nFor Key Figure 2",  "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"))+
  theme(plot.caption = element_text(hjust=c(0, 1))) +
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend

##100 Pcnt bar chart
plot(likert(df_f4.reverse2[,c(1:4)], grouping = df_f4.reverse[,5]), legend.position="right", centered = FALSE, plot.percents=FALSE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE,) +
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = c("NA", "Not sure", "Unacceptable", "Acceptable")) + #order and color the likert boxes
  ggtitle(titlef4) +
    labs(       caption = c("Additional Figure 4.5\nFor Key Figure 2",  "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"))+
  theme(plot.caption = element_text(hjust=c(0, 1))) +
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend
```

@@

First, to echo Bourdieu’s writings, we would like to problematize our use of the idea of “the public” at all; the data we have been manipulating, and the visualizations produced therein, are by no means necessarily representative of “the public.” The public, as we would like to think of it, does not exist. Per the topline we received as part of this data set, the *actual* body of people surveyed is 5,869 members of the American Trends Panel: a national, probability-based online panel of non-institutionalized adults living in households in the United States, including Alaska and Hawaii. The fact that this is a pre-selected, probability-based panel highlights that the body of participants does not encompass every single person living in the United States, nor does every person living in the United States who interacts in some meaningful way with technology and digital privacy fall under those categorizations. Pew Research Center is a meticulous, thorough group known for producing robust data as well as analyses of said data. Though, there will always be blind spots, which we must be mindful of when discussing *what* exactly our work produced.

@@

As we emphasized in the original text introducing key figure 1, there were two factors that we found it extremely important to accurately represent within our visual examining respondents’ stance on digital privacy and personal data: the scale of the difference between counts for the two binary options to `PUBLICDATA_W49`, and the internal distribution for each of those two categories of respondents on the issue of the Right to Be Forgotten.

We chose fairly quickly to forgo what we would think of as the “reverse” of our final visual: a faceted bar chart broken up by the four categories of information that the survey proposed as falling under the Right to Be Forgotten, showing the breakdown of each category of data’s response along the lines of those who prefer public versus private data. Though this visualization would have the advantage of showing a finer-grained understanding of the Right to Be Forgotten (showing each category directly rather than using a dummy variable of sum counts, as we ultimately did) it ultimately did not reveal anything new or interesting about the `PUBLICDATA_W49` responses. Every single response of counts only reflected the same relationship between public and private stances. This helped us narrow down our work to try and prioritize showing internal distinctions between those two categories instead.

A visualization that we considered, but rejected, is one which uses not a dodged bar chart but a stacked one, showing the two categories of public versus private data people as two bars and having those bars be partitioned accordingly to reflect the internal distribution of counts of categories that should be protected. This visualization looks as follows:

```{r central_fig_alt, echo = echoval}
levels(pew$PUBLICDATA_W49) <- c("Find others'\ninformation","Keep their\nown information\nprivate", "Refused")
pew %>% drop_na(PUBLICDATA_W49) %>% drop_na(sumRTBF) %>% filter(PUBLICDATA_W49 != "Refused") %>% ggplot(aes(x = PUBLICDATA_W49, fill = as.factor(sumRTBF))) +
  geom_bar() +
  labs (
    title = "Attitudes on How Many Categories of Data Should Be Protected by\n\"The Right To Be Forgotten\" by Stance on Personal Data",
    x = "Participants find it more important to...",
    y = "",
    caption = c("Alternate Key\nFigure 2",  "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"))+
  theme(plot.caption = element_text(hjust=c(0, 1))) +
  scale_fill_brewer(palette="YlGnBu", name = "How many of the following categories\nof data should fall under the Right To Be Forgotten:\n   -Data collected by law enforcement\n   -Employment history or work record\n   -Negative media coverage\n   -Potentially embarassing photos or\n     videos", labels=c("None","One","Two","Three","Four"))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))
```
This visualization does both things that we would like it to do: it makes immediately apparent the difference in scale between those who prioritize public data versus private, and it has a clear color-coded breakdown of how many categories of data each class thinks should be protected. However, it is clunky and makes it harder to closely examine the distribution of sum counts than it is in our final graphic. As Healy breaks down, bad design is plagued by bad perception; stacking the boxes for each number makes it hard to directly compare the distribution of counts by not having a common base. This in turn warps our perception of the final data. So while this tells a similar story to the one up above, we ended up making additional aesthetic decisions to better convey that information in a clear and pleasing way.

@@

Jake and Adriana split the project evenly. While they both were the lead on their respective key figures, they shared code snippets, analytical choices, and design tips. Unless explicitly split by key figure, Adriana and Jake discussed and drafted each essay section of the appendix together while Adriana transformed the drafts into a well written final project. To keep the workload fair, Jake worked on debugging and formatting the final submission.
